Digitization of the Australian Parliamentary Debates, 1901-2022^[Code is available at: https://github.com/lindsaykatz/hansard-proj, data is available at https://doi.org/10.5281/zenodo.7336076]

### 2023-02-03 paper/paper.qmd
lots of updates

---
title: "Digitization of the Australian Parliamentary Debates (1901-2022)^[Code is available at: https://github.com/lindsaykatz/hansard-proj]"
number-sections: true
format: 
  pdf:
    keep-tex: true
bibliography: references.bib
editor: visual
date: "now"
date-format: long
author:
  - Lindsay Katz^[University of Toronto, lindsay.katz@mail.utoronto.ca]
  - Rohan Alexander^[University of Toronto, rohan.alexander@utoronto.ca]
abstract: "Public knowledge of what is said in parliament is a key tenet of democracy. Parliamentary dialogue is also critical for political science research. In Australia, following the UK tradition, the written record of what is said in parliament is known as Hansard. While the Australian Hansard has always been publicly available, it has been difficult to use it for the purpose of large-scale macro and micro-level text analysis because it has not been available as a dataset of sufficient quality to be credibly analysed with statistical models. Following the lead of the LiPaD project which achieved this for Canada, our project aims to provide a new, comprehensive, high-quality database that captures all proceedings of the Australian parliamentary debates from 1901 to the present day using Hansard. Our dataset will be publicly available and linked to other datasets such as election results. The creation of this dataset will enable the exploration of questions that are not currently possible to explore, serving as a valuable resource for both researchers and policymakers. This work will provide a thorough description of the creation and computational underpinnings of this database, followed by a discussion of some applications. To this point, we have completed this for 2011 to 2022."
---

# Introduction {#sec-intro}

@@

The end goal for this work is to create a publicly available database of parsed Hansard transcripts from 1901 to present in a form which can be readily analyzed. More specifically, we aim to present each transcript in an ordered form with details on each speaker such as their political affiliation, the time stamp of their statement (where available), and whether they interjected (i.e. spoke out of turn). Thus far, this has been done for Hansard from mid-2011 to present.

@@

# Existing Datasets {#sec-existing}

@@

# Description of the Database {#sec-description}

Our current database contains 670 comma-separated values (CSV) files, one for each sitting day of the House of Representatives from 10 May 2011 to 08 September 2022. We used two scripts to produce these files, which only have one subtle difference. Since the Federation Chamber was renamed in mid-2012 from the original title of Main Committee, the element under which all the Federation Chamber contents are nested in the XML was renamed as well [@australia2018house, ch. 21]. This difference in element name means that our original code for parsing Federation Chamber content would not work, as the specified node path would be incorrect. We accounted for this by creating a separate script with this name change. Our first script parses Hansard from 14 August 2012 to 08 September 2022, that being everything after the Federation Chamber name change, and the second script parses Hansard from 10 May 2011 to 28 June 2012. All output files in our database are formatted and processed in the exact same way. @fig-main15rows provides a snapshot of one of these files.

@@

@@

# Creation of the Database {#sec-create}

@@

# References

>>>>

---
title: "Digitization of the Australian Parliamentary Debates, 1901-2022^[Code is available at: https://github.com/lindsaykatz/hansard-proj, data is available at https://doi.org/10.5281/zenodo.7336076]"
number-sections: true
format: 
  pdf:
    keep-tex: true
bibliography: references.bib
editor: visual
date: "now"
date-format: long
author:
  - Lindsay Katz^[University of Toronto, lindsay.katz@mail.utoronto.ca]
  - Rohan Alexander^[University of Toronto, rohan.alexander@utoronto.ca]
abstract: "Public knowledge of what is said in parliament is a key tenet of democracy, and such parliamentary dialogue is critical for political science research. In Australia, following the British tradition, the written record of what is said in parliament is known as Hansard. While the Australian Hansard has always been publicly available, it has been difficult to use it for the purpose of large-scale macro and micro-level text analysis because it has not been available as a dataset of sufficient quality to be credibly analysed with statistical models. Following the lead of the Linked Parliamentary Data project which achieved this for Canada, our project aims to provide a new, comprehensive, high-quality database that captures all proceedings of the Australian parliamentary debates from 1901 to the present day using Hansard. Our dataset will be publicly available and linked to other datasets such as election results. The creation of this dataset will enable the exploration of questions that are not currently possible to explore, serving as a valuable resource for both researchers and policymakers. This work will provide a thorough description of the creation and computational underpinnings of this database, followed by a discussion of some applications. To this point, we have completed this for 1998 to 2022."
---

# Background & Summary {#sec-intro}

@@

The end goal for this work is to create a publicly available database of parsed Hansard transcripts from 1901 to present in a form which can be readily analyzed. More specifically, we aim to present each transcript in an ordered form with details on each speaker such as their political affiliation, the time stamp of their statement (where available), and whether they interjected (i.e. spoke out of turn). Thus far, this has been done for Hansard from 1998 to present.

@@

## Existing Datasets {#sec-existing}
*NOTE: THERE AREN'T ALLOWED TO BE SUBSECTIONS IN THIS FIRST SECTION, SO REMOVE THIS HEADING*

@@

# Methods

Our current database contains 1516 comma-separated values (CSV) files, one for each sitting day of the House of Representatives from 02 March 1998 to 08 September 2022. We created four scripts to produce these files. As we worked backwards in time, the first script we developed parses everything from 14 August 2012 to 08 September 2022. The second script parses Hansard from 10 May 2011 to 28 June 2012, and the third script parses Hansard from 15 February 2000 to 24 March 2011. The fourth and final script parses Hansard for every sitting day in 1998 and 1999. In summary, these four scripts parse all available XML Hansard records for the House of Representatives from 1998 to the present.

While all scripts use the same approach and produce the same structure of data record, the first and second script use a slightly different method of data cleaning

structural variation in XML over time necessitated the production of unique scripts to parse different time frames.

The first and second scripts are very similar in structure, with one subtle difference.

The third and fourth scripts are very similar to one another.

The biggest difference between these scripts

The first two scripts only have one subtle difference

Since the Federation Chamber was renamed in mid-2012 from the original title of Main Committee, the element under which all the Federation Chamber contents are nested in the XML was renamed as well [@australia2018house, ch. 21]. This difference in element name means that our original code for parsing Federation Chamber content would not work, as the specified node path would be incorrect. We accounted for this by creating a separate script with this name change. Our first script parses Hansard from 14 August 2012 to 08 September 2022, that being everything after the Federation Chamber name change, and the second script parses Hansard from 10 May 2011 to 28 June 2012. All output files in our database are formatted and processed in the exact same way. @fig-main15rows provides a snapshot of one of these files.

@@

# Data Records

@@

@@

# Usage notes
# Code availability
# Acknowledgements
# Author contributions
# Competing interests
# References
